---
title: "DV Assignment 2: [Your Title Here]"
author: "Group X: Firstname Lastname, Firstname Lastname, Firstname Lastname"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls()) # clear environment so knitting only depends on what's in this file

# installs (if missing) and loads every package this project uses - add any
# new packages to scripts/00-packages.R, not here
source("../scripts/00-packages.R")

# downloads the data into data/raw/ if you don't already have it, then loads
# eindscores, referentieniveaus, schooladviezen and schoolweging into this
# session - see scripts/01-get-data.R for what each one contains
source(here("scripts", "01-get-data.R"))
```

## Research question

*What are you investigating, and why does it matter? Who is the target audience for your final visualization, and how does that shape your choices?*

## Exploratory process

*Describe how you explored the data before settling on your final visualization. Include at least one exploratory plot below, and a short note on what it told you (or didn't).*

```{r exploratory-plot}

```

## Final visualization

*Your final, explanatory visualization goes below. Include a short write-up: what does it communicate, why is this the best way to communicate it, and how robust is the finding?*

```{r final-plot}

```

## Conclusion

*What can you conclude from your visualization? What are the limitations of this analysis?*

---

**Before submitting:** run the lintr check on this file, and re-knit from a clean environment (`rm(list = ls())`, already done above) to make sure everything reproduces from scratch.
